Fluoroproj: Title to be decided later

### 2023-04-14 manuscript/manuscript_sds.qmd
updated introduction

A variety of instruments have been developed to measure chlorophyll a and/or phycocyanin without an extraction step and have a wide range in cost. Most of these instruments rely on in vivo fluoroescense and can be used in the field or the lab, or a combination of both.

@@

Field instruments may be placed directly in a waterbody or require water to be poured into a cuvette and then placed into a handheld fluorometer. Differences in measurement methods represent a potential source of error when comparing instruments. Additionally, instruments may report valued in rfus (raw or relative fluorescence units) or µg/L (concentration) and comparing these values introduces an additional source of error during comparison.

The goal of this paper is to compare different handheld or in situ fluorometers with respect to a common benchmark (extracted chlorophyll and phycocyanin) in order to provide a communications tool for groups using these different instruments.

>>>>

A variety of instruments have been developed to measure chlorophyll a and/or phycocyanin using in vivo fluorescence without an extraction step and have a wide range in cost. These instruments distinguish between the pigments based on their differing emission spectra. Some instruments (i.e. PhycoProbe) use multiple leds at varying wavelengths to cause fluorescence of different algal types, thus creating a finer scale breakdown of community composition. These instruments can be used in the field, the lab, or a combination of both.

@@

Field instruments may be placed directly in a waterbody or require water to be poured into a cuvette and then placed into a handheld fluorometer. Differences in measurement methods represent a potential source of error when comparing instruments. Additionally, instruments may report valued in rfus (raw or relative fluorescence units) or µg/L (concentration) and comparing these values introduces an additional source of error during comparison. In vivo fluorescence can be affected by photochemical quenching causing an underestimation of rfus as photosystems become saturated with light. Estimation problems can also result from differing community composition, particularly if colonial cyanobacteria are present as the interior of large colonies will not fluoresce as readily as the exterior. Finally, the physical properties of the sample water can greatly affect fluorescence readings based on turbidity levels and the presence of CDOM. Some instruments offer a yellow substance correction to help account for CDOM while others do not. How the different instruments handle these various potential problems can affect their accuracy, precision, and the ability to compare across different instrument types. The goal of this paper is to compare different handheld or in situ fluorometers with respect to a common benchmark (extracted chlorophyll and phycocyanin) in order to provide a communications tool for groups using these different instruments.
